|

### 2020-01-13 nontex/install/windows/fn_installations.Rmd
rerun install file html and pdf

---
title: |
  | New Computer Fan Data-Science Set-up
  | Python (Anaconda), R (Rstudio), Matlab and Latex (Texlive)
  | Atom, VScode, Pycharm
output:
  html_document:
    number_sections: true
  html_notebook:
    number_sections: true
  word_document:
    number_sections: true
  pdf_document:
    df_print: paged
    number_sections: true
urlcolor: blue
always_allow_html: yes
---

>>>>

---
title: |
  | New Computer Fan Data-Science Set-up
  | Python (Anaconda), R (Rstudio), Matlab and Latex (Texlive)
  | Atom, VScode, Pycharm
output:
  pdf_document:
    df_print: paged
    number_sections: true
  html_notebook:
    number_sections: true
  word_document:
    number_sections: true
  html_document:
    number_sections: true
urlcolor: blue
always_allow_html: yes
---
